GMSE: an R package for generalised management strategy evaluation

### 2018-05-10 notebook/ms/ms.Rmd
Minor edits
Add acknowledgements

|  res_birth_K    |  10000  | Carrying capacity applied to the number of resources added during a time step                    |

@@

>>>>

|  res_birth_K    |  100000 | Carrying capacity applied to the number of resources added during a time step                    |

@@

Conclusions
===================================================

Acknowledgements
===================================================

This project was funded by the European Research Council under the European Union's H2020/ERC grant agreement no. 679651 (ConFooBio) to NB. ABD is funded by a Leverhulme Trust Early Career Fellowship. We thank two anonymous reviewers for very helpful comments.
